Fisheries management when quotas are costly to change

### 2014-07-31 manuscripts/presentation.Rmd
tweak layout

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
revealjs-url:  "./presentation_files/reveal.js-2.6.1"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: false
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

<!-- 
Time: 30 minutes with questions
Presenting at: 2014-12-08 15:10:00 PDT
-->

>>>>

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: false
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth

notes: |
  Time: 30 minutes with questions
  Presenting at: 2014-12-08 15:10:00 PDT

@@
